Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-10 paper-kelompok/main.tex

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.

\section*{Acknowledgement}
The authors thank Dr. Isa Anshori from Department of Biomedical Engineering, Institut Teknologi Bandung and his research team for assistance with DMF integration and sample preparation.
This work was funded by Department of Electrical Engineering, Institut Teknologi Bandung.

>>>>

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Thermo Scientific™ Evolution 220).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.

\section*{Acknowledgement}
This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.

\section*{References}
